Extracorporeal CPR for Refractory Out-of-Hospital Cardiac Arrest \\\large{A Bayesian Perspective}

### 2023-02-07 manuscript/manuscript.qmd
2nd Bayesian with priors only for Tx

library(here)
library(tidyverse)
library(broom)
library(cobalt)
library(table1)
library(knitr)
library(patchwork)
library(rstanarm)
library(tidybayes)

@@

library(gt)
gt(table_tbl) %>%
  tab_stubhead(label = "Priors") 
```

@@

>>>>

library(here)
library(tidyverse)
library(broom)
library(cobalt)
library(table1)
library(knitr)
library(patchwork)
library(rstanarm)
library(tidybayes)
library(gt)

@@

gt(table_tbl) %>%
  tab_stubhead(label = "Priors") 
```

@@

Update 2023/02/07
Might make most sense to interpret the INCEPTION trial based on the baseline CPR risk observed in that trial and provide informative priors only for the Tx variable (enthusiastic from ARREST, skeptical from PRAGUE)

# Bayesian prior analysis #2
```{r}
## try re-running using prior for eCPR from different studies but leaving CPR with vague prior since baseline risks with CPR seem to vary
## widely btw the different studies

eCRP_bayes_no_intercept_prior <- function(data, m_eCPR, sd_eCPR ) {
  set.seed(1234)
  fit <- stan_glm(prop_success ~ Tx, data = data, family = binomial(link="logit"), weights = total, refresh=0,
                  prior = normal(m_eCPR, sd_eCPR))
  fit_sum <- summary(fit, digits=3)
  conf_95 <- c(exp(fit_sum[2]),exp(fit_sum[2]+c(-1,1)*1.96*fit_sum[10]))
  tt <- fit %>%
    spread_draws(`(Intercept)`, `TxeCPR`)
  fig_prob <- sum(tt$TxeCPR>0)/nrow(tt)
  fit_draws <- fit %>% tidybayes::tidy_draws() 
  my_list <- list(fig_prob, conf_95, fit_draws)
  return(my_list)
}

comb_prior1 <-eCRP_bayes_no_intercept_prior(df[c(1:2),], comb_m_eCPR, comb_sd_eCPR) #stan_glm with combined prior
enth_prior1 <- eCRP_bayes_no_intercept_prior(df[c(1:2),], enth_m_eCPR, enth_sd_eCPR) #stan_glm with enthusiastic prior
skep_prior1 <- eCRP_bayes_no_intercept_prior(df[c(1:2),], skep_m_eCPR, skep_sd_eCPR) #stan_glm with skeptical prior

table_tbl_1 <- 
  tibble(
    prior = c("vague", "combined", "enthusiastic", "skeptical"),
    pt_est <- c(conf_95[1], comb_prior1[[2]][1], enth_prior1[[2]][1], skep_prior1[[2]][1]),
    llimit <- c(conf_95[2], comb_prior1[[2]][2], enth_prior1[[2]][2], skep_prior1[[2]][2]),
    ulimit <- c(conf_95[3], comb_prior1[[2]][3], enth_prior1[[2]][3], skep_prior1[[2]][3]),
    p.gt.1 <- c(fig_prob, comb_prior[1], enth_prior[1], skep_prior[1])
  )

gt(table_tbl_1) %>%
  tab_stubhead(label = "Priors") 
```

This seems like a reasonable solution

### 2023-02-07 manuscript/manuscript.tex
2nd Bayesian with priors only for Tx

\begin{keyword}
    extracorporeal CPR \sep 
    Bayesian statistics
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

@@

@@

\includegraphics{manuscript_files/figure-pdf/unnamed-chunk-4-1.pdf}

>>>>

\begin{keyword}
    extracorporeal CPR \sep 
    Bayesian statistics
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

@@

Update 2023/02/07 Might make most sense to interpret the INCEPTION trial
based on the baseline CPR risk observed in that trial and provide
informative priors only for the Tx variable (enthusiastic from ARREST,
skeptical from PRAGUE)

\hypertarget{bayesian-prior-analysis-2}{%
\section{Bayesian prior analysis \#2}\label{bayesian-prior-analysis-2}}

\begin{longtable}{lrrrc}
\toprule
prior & pt\_est <- ... & llimit <- ... & ulimit <- ... & p.gt.1 <- ... \\ 
\midrule
vague & 1.32 & 0.543 & 3.21 & 0.727 \\ 
combined & 1.35 & 0.705 & 2.58 & 0.782 \\ 
enthusiastic & 1.40 & 0.738 & 2.67 & 0.79 \\ 
skeptical & 1.32 & 0.700 & 2.50 & 0.777 \\ 
\bottomrule
\end{longtable}

This seems like a reasonable solution

@@

\includegraphics{manuscript_files/figure-pdf/unnamed-chunk-5-1.pdf}
